---
title: "Reproducible Research: PA1"
author: "Filip Floegel"
date: "Saturday, January 17, 2015"
output: html_document
---

First I will set the working directory, loading data, loding the package plyr for ddply

```{r, echo=TRUE}
setwd("C:/Users/Filip/coursera/data science/Reproducible Research/RepData_PeerAssessment1")
activity <- read.csv("./activity.csv", header=TRUE)
library(plyr)
```

# What is mean total number of steps taken per day?
first counting the nbr of steps each day

```{r, echo=TRUE}
nbr_steps_date <- ddply(activity, ~date, summarize, nbr_steps=sum(steps), mean_steps=mean(steps), med_steps=median(steps))
with(nbr_steps_date,plot( date, nbr_steps, type="l"))
```

Now lets calc the mean of nbr of steps per day

```{r, echo=TRUE}
mean(nbr_steps_date$nbr_steps, na.rm=TRUE)
```

and the median of nbr of steps per day

```{r, echo=TRUE}
median(nbr_steps_date$nbr_steps, na.rm=TRUE)
```

# What is the average daily activity pattern?

# Imputing missing values

# Are there differences in activity patterns between weekdays and weekends?
