---
title: "Reproducible Research: PA1"
author: "Filip Floegel"
date: "Saturday, January 17, 2015"
output: html_document
---

First I will set the working directory, loading data, loding the package plyr for ddply

```{r, echo=TRUE}
setwd("C:/Users/Filip/coursera/data science/Reproducible Research/RepData_PeerAssessment1")
activity <- read.csv("./activity.csv", header=TRUE)
library(plyr)
```

# What is mean total number of steps taken per day?
first counting the nbr of steps each day

```{r, echo=TRUE}
nbr_steps_date <- ddply(activity, ~date, summarize, nbr_steps=sum(steps), mean_steps=mean(steps), med_steps=median(steps))
with(nbr_steps_date,plot( date, nbr_steps, type="l"))
```

Now lets calc the mean of nbr of steps per day

```{r, echo=TRUE}
mean_steps <- mean(nbr_steps_date$nbr_steps, na.rm=TRUE)
mean_steps
```

and the median of nbr of steps per day

```{r, echo=TRUE}
med_steps <- median(nbr_steps_date$nbr_steps, na.rm=TRUE)
med_steps
```

# What is the average daily activity pattern?

first the average. be aware of the missing values within steps

```{r, echo=TRUE}
avg_steps_int <- ddply(activity, ~interval, summarize, avg_steps=mean(steps, na.rm=TRUE), nbr_steps=sum(steps, na.rm=TRUE))
```

Now, lets take a library ggplot for a nice time series plot and plot the average steps per intervall for all dates 

```{r, echo=TRUE}
library(ggplot2)
p <- ggplot(avg_steps_int, aes(x=interval, y=avg_steps))
p + geom_line()
```

# Imputing missing values

first counting the total nbr of rows with missing values by calculating the nbr of rows - the sumber of complete cases

```{r, echo=TRUE}
nrow(activity) - sum(complete.cases(activity))
```

use avg nbr of steps in nbr_steps_int in order to impute the missings steps. first step merge the two table using merge by interval

```{r, echo=TRUE}
act_imp <- merge(activity, avg_steps_int[,c("interval","avg_steps")], by.x="interval", all=TRUE)
imp_steps <- apply(act_imp, 1,function(x) {ifelse(is.na(x["steps"]),round(as.numeric(x["avg_steps"])),as.numeric(x["steps"]))})
activity$imp_steps <- imp_steps
```

### 4. total number of steps taken each day and...

```{r, echo=TRUE}
nbr_imp_steps_date <- ddply(activity, ~date, summarize, nbr_imp_steps=sum(imp_steps))
```

### 4. Calculate and report the mean and median total number of steps taken per day.

first mean

```{r, echo=TRUE}
mean_imp_steps <- mean(nbr_imp_steps_date$nbr_imp_steps, na.rm=TRUE)
mean_imp_steps
```

and the median of nbr of steps per day

```{r, echo=TRUE}
med_imp_steps <- median(nbr_imp_steps_date$nbr_imp_steps, na.rm=TRUE)
med_imp_steps
```

### 4. Do these values differ from the estimates from the first part of the assignment? 

```{r, echo=TRUE}
mean_steps - mean_imp_steps
med_steps - med_imp_steps
```

The mean of steps dont differs from the mean of imputed steps but the median does differ.

### 4. Make a histogram of the total number of steps taken each day and...

What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r, echo=TRUE}
with(nbr_imp_steps_date,plot( date, nbr_imp_steps, type="l"))
```

well the total nbr of steps per day looks pretty much the same as the picture of the timeries above wich is for sure not right!

her another check of the imputed new variable imP_steps... comparison with the timeseries plot!

```{r, echo=TRUE}
avg_imp_steps_int <- ddply(activity, ~interval, summarize, avg_steps=mean(imp_steps))
p <- ggplot(avg_imp_steps_int, aes(x=interval, y=avg_steps))
p + geom_line()
```

well, doesnt look the same at all :-(


# Are there differences in activity patterns between weekdays and weekends?
